---
title: "Causality - MDD"
author: "Black Swan - Capstone Group"
date: "April 13, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_knit$set(root.dir = getwd())

#install.packages("fastDummies")
#install.packages("erer") # save list as .csv
#install.packages("AER")
library(fastDummies)
library(data.table)
library(erer)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(tidyverse)
library(lubridate)
library(plm) # panel model
library(AER) # IV regression
library(stargazer) # tables for output regression
library(lmtest) # robust standard error

# Pallete 
cbPalette <- c("#164D73", "#F7BD36", "#E04E70", "#164D73", "#8B8F9A")
# Basic charts specs 
myattributes <- theme_bw() +
                theme(panel.border = element_blank(), 
                      panel.grid.major = element_blank(), 
                      panel.grid.minor = element_blank(), 
                      axis.line = element_line(color = "grey"), 
                      axis.ticks.x = element_blank(), 
                      axis.ticks.y = element_blank(),
                      plot.caption=element_text(size=9,
                                                color = "grey"))


```

0. Database
```{r database}
# Importing database
db <- read.csv("esg_scores_8Feb.csv")

# Selecting variables for causality model
vars <- c("ï..company_id", "name", "region", "gics_sector", "gics_industry", "size", "value_date", "ESG", "E", "S", "G", "mdd_1m","mdd_3m", "mdd_6m",  "mdd_1y", "mdd_18m", "mdd_3y")

dat <- db  %>% select(vars)

```

1. Preparing data
```{r}

dat <- dummy_cols(dat, select_columns = "gics_sector")
setnames(dat, old=c("gics_sector_Communication Services", "gics_sector_Consumer Discretionary", 
                   "gics_sector_Consumer Staples", "gics_sector_Energy", "gics_sector_Financials", 
                   "gics_sector_Health Care", "gics_sector_Industrials", 
                   "gics_sector_Information Technology", "gics_sector_Materials", 
                   "gics_sector_Real Estate", "gics_sector_Utilities"), 
         new=c("Communication", "ConsumerDiscret", "ConsumerStaples", "Energy", "Financials", 
               "HealthCare", "Industrial", "IT", "Materials", "RealEstate", "Utilities"))

dat <- dummy_cols(dat, select_columns = "region")
setnames(dat, old=c("region_Europe", "region_North America", "region_Asia Pacific", 
                   "region_Middle East and Africa", "region_Latin America and Caribbean"), 
       new=c("Europe", "NorthAmerica", "AsiaPacific", "AfricaMiddleEast", "LatinAmericaCaribbean"))

dat <- dummy_cols(dat, select_columns = "size")
setnames(dat, old=c("size_Large", "size_Mid", "size_Small"), 
         new=c("Large", "Mid", "Small"))

dat$date <- as.Date(dat$value_date, format="%m/%d/%Y")

# organizing dataframe
setnames(dat, old=c("ï..company_id"), new=c("id"))
dat <- dat %>% select(-region, -gics_sector, -size, -value_date)
dat <- dat %>% select("id", "name", "date", everything())

```


2. Analyzing data
We are going to use a list of corporate scandals. So far, the list of scandals comes from an IG news, "Top 10 biggest corporate scandals and how they affected share prices".
```{r}
# Mean of ESG and MDD before and after the shock

shockAnalysis <- function(company, target, shockPropagation){
  
  industry <- unique(dat$gics_industry[dat$name==company])
  tgtCorrect <- ifelse(str_sub(target,-2,-1)=="1m",1, ifelse(
    str_sub(target,-2,-1)=="3m",3, ifelse(
      str_sub(target,-2,-1)=="6m",6, ifelse(
        str_sub(target,-2,-1)=="1y",12, ifelse(
          str_sub(target,-3,-1)=="18m",18, ifelse(
            str_sub(target,-2,-1)=="3y",36,"Error"
  ))))))
  shockDate <- unique(shocks$shockDate[shocks$company==company])
  
  # Company affected by shock
  pre <- dat %>% subset(name==company & 
                          date>as.Date(shockDate) %m-% months(tgtCorrect) %m-% months(shockPropagation) &
                          date<as.Date(shockDate) %m-% months(tgtCorrect)) %>% 
    summarise(ESG=mean(ESG, na.rm = TRUE), 
              MDD=mean(eval(parse(text=target)), na.rm = TRUE))
  pre <- cbind(company, industry, pre, target, shockPropagation, shockDate)
  
  post <- dat %>% subset(name==company & 
                           date>as.Date(shockDate) & 
                           date<as.Date(shockDate) %m+% months(shockPropagation)) %>% 
    summarise(ESG=mean(ESG, na.rm = TRUE), 
              MDD=mean(eval(parse(text=target)), na.rm = TRUE))
  post <- cbind(company, industry, post, target, shockPropagation, shockDate)
  
  tblShockComp <- rbind(PreShock_Company=pre, PostShock_Company=post)
  
  # Remaining industry ESG and performance
  pre <- dat %>% subset(gics_industry==industry & 
                          date>=as.Date(shockDate) %m-% months(tgtCorrect) %m-% months(shockPropagation) &
                          date<as.Date(shockDate) %m-% months(tgtCorrect)  & 
                          name != company) %>% 
    summarise(ESG=mean(ESG, na.rm = TRUE), 
              MDD=mean(eval(parse(text=target)), na.rm = TRUE))
  pre <- cbind(company, industry, pre, target, shockPropagation, shockDate)
  
  
  post <- dat %>% subset(gics_industry==industry & 
                           date>=as.Date(shockDate) & 
                           date<=as.Date(shockDate) %m+% months(shockPropagation) & 
                           name != company) %>% 
    summarise(ESG=mean(ESG, na.rm = TRUE), 
              MDD=mean(eval(parse(text=target)), na.rm = TRUE))
  post <- cbind(company, industry, post, target, shockPropagation, shockDate)
  
  tblShockInd <- rbind(PreShock_RemainingIndustry=pre, PostShock_RemainingIndustry=post)
  
  tblShock <- rbind(tblShockComp, tblShockInd)
  return(tblShock)
  
}

# run function
shocks <- read.csv("shocks.csv")
shocks$shockDate <- as.Date(shocks$shockDate, format="%m/%d/%Y")

shockAnalysisList <- lapply(
  as.vector(shocks$companyName), function(x){
    lapply(
      c(3,6), function(y){
        shockAnalysis(company = x, target = "mdd_6m", shockPropagation = y)
        })
    })

write.list(shockAnalysisList, "shockAnalysisList1.csv", row.names = TRUE)

```

FUNCTION: Build database function for IV Model
```{r}
############ START: Function to build data for IV model ############
shockData <- function(company, target, shockPropagation){
  # inputs of shocks: company, data, target variable and shock propagation (months persistence)
  industry <- unique(dat$gics_industry[dat$name==company])
  shockDate <- unique(shocks$shockDate[shocks$company==company])
  tgtCorrect <- ifelse(str_sub(target,-2,-1)=="1m",1, ifelse(
      str_sub(target,-2,-1)=="3m",3, ifelse(
        str_sub(target,-2,-1)=="6m",6, ifelse(
          str_sub(target,-2,-1)=="1y",12, ifelse(
            str_sub(target,-3,-1)=="18m",18, ifelse(
              str_sub(target,-2,-1)=="3y",36,"Error"
    ))))))
  
  
  # computation of ESG and mdd mean before the shock
  pre <- dat %>% subset(date>=(as.Date(shockDate) %m-% months(tgtCorrect) %m-%
                                 months(shockPropagation)) &
                          date<(as.Date(shockDate) %m-% months(tgtCorrect))) %>%
    group_by(id) %>% 
    summarise(ESG=mean(ESG, na.rm = TRUE), 
              mdd=mean(eval(parse(text=target)), na.rm = TRUE))
  # combining with variables necessary to the IV regression and adding date of pre-shock period and dummy of the shock (in this case = 0, since it is before shock)
  pre <- pre %>% 
    inner_join(vars_dat, by = "id")
  pre <- pre %>% 
    cbind(date=as.Date(shockDate) %m-% months(1), 
          d_Industry=ifelse(pre$gics_industry==industry,1,0),
          d_Shock=0,
          d_IndustryShock=0,
          d_CompanyShock=ifelse(pre$name==company,1,0),
          shockName=company)
  
  # computation of ESG and mdd mean after the shock
  post <- dat %>% subset(date>=as.Date(shockDate) &
                          date<as.Date(shockDate) %m+% months(shockPropagation)) %>%
    group_by(id) %>% 
    summarise(ESG=mean(ESG, na.rm = TRUE), 
              mdd=mean(eval(parse(text=target)), na.rm = TRUE))
  # combining with variables necessary to the IV regression and adding date of shock period and dummy of the shock (in this case = 1, if it is any company of the sector of the company that suffered the shock. The company that suffered the shock is 0)
  post <- post %>% 
    inner_join(vars_dat, by = "id")
  post <- post %>% 
    cbind(date=as.Date(shockDate), 
          d_Industry=ifelse(post$gics_industry==industry,1,0),
          d_Shock = 1,
          d_IndustryShock=ifelse(post$gics_industry==industry,1,0), # & post$name!=company,
          d_CompanyShock=ifelse(post$name==company,1,0),
          shockName=company) 
 
  prePost <- rbind(pre, post)
  return(prePost)
}
############ END: Function to build data for IV model ############

# variables necessary to IV regression
vars_dat <-
  dat %>%
  select(-c(date, ESG, E, S, G, mdd_1m, mdd_3m, mdd_6m, mdd_1y, mdd_18m, mdd_3y)) %>%
  unique()

```


3. Run the fucntion to create database for IV Model. Choose the shocks, target variable and shock persistence
```{r}
############ Run function to create data frame
# list of shocks
shocks <- read.csv("shocks.csv")
shocks$shockDate <- as.Date(shocks$shockDate, format="%m/%d/%Y")
shockList <- as.vector(shocks$companyName)
#shockList <- "Volkswagen AG"

datMod <- data.frame()
for (i in shockList) {
  res <- shockData(company = i, target = "mdd_3m", shockPropagation = 3)
  datMod <- rbind(datMod, res)
}

# there are some mdd=0. Remove to allow us to take the log
datMod <- datMod %>% subset(mdd>0) 

# some data analysis
shockSummary <- datMod %>% 
 group_by(shockName, d_CompanyShock, d_IndustryShock) %>%  
 summarise(mean(ESG, na.rm = TRUE), mean(mdd, na.rm = TRUE))

writexl::write_xlsx(shockSummary, "shockSummary_06m03p.xlsx")

```

FUNCTION: Build Function for robust SE and diagnostic output
```{r}
# Robust SE function for stargazer
gaze.coeft <- function(x, col="Std. Error"){
    stopifnot(is.list(x))
    out <- lapply(x, function(y){
        y[ , col]
    })
    return(out)
}

# Diagnostic function for stargazer
gaze.lines.ivreg.diagn <- function(x, col="p-value", row=1:3, digits=2){
    stopifnot(is.list(x))
    out <- lapply(x, function(y){
        stopifnot(class(y)=="summary.ivreg")
        y$diagnostics[row, col, drop=FALSE]
    })
    out <- as.list(data.frame(t(as.data.frame(out)), check.names = FALSE))
    for(i in 1:length(out)){
        out[[i]] <- c(names(out)[i], round(out[[i]], digits=digits))
    }
    return(out)
}


```


4. IV regression
```{r}
# Model for each shock
modListIV <- lapply(shockList, function(x){
  ivreg((mdd) ~ (ESG) + Europe + NorthAmerica + 
          AsiaPacific + AfricaMiddleEast + LatinAmericaCaribbean + 
          Mid + Large + Small | 
          d_IndustryShock + Europe + NorthAmerica + 
          AsiaPacific + AfricaMiddleEast + LatinAmericaCaribbean + Mid + Large + Small, 
        data = subset(datMod, shockName==x & d_Industry==1))
})
modListIV <- setNames(modListIV, shockList)

# Summary with the diagnostic and exchange the normal standard errors with robust standard errors
robustSEList <- lapply(modListIV, function(i) { 
  coeftest(i, function(x) vcovHC(x, type="HC0"))
  })

diagnosticList <- lapply(modListIV, function(i){
  summary(i, vcov. = function(x) vcovHC(x, type="HC0"), diagnostics=T)
  })


# Output using Stargazer
Out_ModList_IV <- stargazer(modListIV, type = "text", title="IV Regression", align = TRUE,
                            dep.var.labels=c("Maximum-Drawdown 1-month (MDD)"),
                            se = gaze.coeft(robustSEList), 
                            add.lines = gaze.lines.ivreg.diagn(diagnosticList, row=1:2),
                            out = "Out_ModList_IV_03m03p.html")

summary(modListIV[[3]])
modListIV

```


5. Linear model and first stage
```{r}
### Linear Regression: ESG to explain MDD - Linear regression on MDD
modListLM <- lapply(shockList, function(x){
  lm((mdd) ~ (ESG) + Europe + NorthAmerica + 
          AsiaPacific + AfricaMiddleEast + LatinAmericaCaribbean + 
          Mid + Large + Small, 
        data = subset(datMod, shockName==x & d_Industry==1))
})
modListLM <- setNames(modListLM, shockList)

# Output using Stargazer
Out_ModList_LM <- stargazer(modListLM, type = "text", title = "Linear Regression", align = TRUE,
                            dep.var.labels=c("Maximum-Drawdown 1-year (MDD)"),
                            out = "Out_ModList_LM_01y01p.html")


### First stage: shock to explain ESG, but not stocks - Linear regression on ESG
modListFirst <- lapply(shockList, function(x){
  lm((ESG) ~ d_IndustryShock + Europe + NorthAmerica + 
          AsiaPacific + AfricaMiddleEast + LatinAmericaCaribbean + 
          Mid + Large + Small, 
        data = subset(datMod, shockName==x & d_Industry==1))
})
modListFirst <- setNames(modListFirst, shockList)

# Output using Stargazer
Out_ModList_First <- stargazer(modListFirst, type = "text", title = "IV First Stage Regression", align = TRUE,
                            dep.var.labels=c("ESG Score"),
                            out = "Out_ModList_First_01y01p.html")


```

